---
title: 'Class 02: R Intro'
author: "Sarah Sizemore"
date: "2026-02-02"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
    theme: simplex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment

R has three assignment operators: 

- `->`,
- `=`, and
- `<-`

```{r assignments}
x1 = 5
5-> x2
x3 = 7

cat("The value of x1 is", x1)
```

## Atomic Vectors

Atomic vectors are 1D data structures, where all values in them have to have the same data type. For example, if we do the following: 

``` {r atomi, results='hold'}
mixed_vec = c('ISA', 401)
mixed_num = c(401L, 3.14)

print(typeof(mixed_num))
print(typeof(mixed_vec))
```

From this output, if you have multiple data types, R will use the most general representation for them.

## Lists

Sub-setting a list is one of the most common sources of errors in ISA 401

```{r}
lst <- list( # list constructor/creator
  1:3, # atomic double/numeric vector  of length = 3
  "a", # atomic character vector of length = 1 (aka scalar)
  c(TRUE, FALSE, TRUE), # atomic logical vector of length = 3
  c(2.3, 5.9) # atomic double/numeric vector of length =3
)
lst # printing the list


```
